\section{About Version Control}
\begin{enumerate}
    \item What is the big weakness of Centralized Version Control?
    \item In distributed version control, why is there no longer one point 
        of failure?
\end{enumerate}

\section{A Short History of Git}
\begin{enumerate}
    \item Which community was motivated to create a new version control
        tool?
    \item When was Git created?
\end{enumerate}

\section{What is Git?}
\begin{enumerate}
    \item Does Git store snapshots or differences?
    \item Do you need to be online to use Git?
    \item What are the three states that files in a repository can reside 
        in?
\end{enumerate}

\section{The Command Line}
\begin{enumerate}
    \item Where is the only place you can rull all Git commands?
\end{enumerate}

\section{Installing Git}
\begin{enumerate}
    \item What version of Git are you running?
\end{enumerate}

\section{First-Time Git Setup}
\begin{enumerate}
    \item What's the difference between \verb+--global+ and \verb+--system+
        when running \verb+git config+?
    \item Why might you need to check your configuration settings?
    \item Set up your git config
        \begin{enumerate}
            \item Name
            \item Email
        \end{enumerate}
    \item Verify that your name is correctly configured with 
        \verb+git config+
\end{enumerate}

\section{Getting Help}
\begin{enumerate}
    \item Use \verb+git help+ to answer the following:
        \begin{enumerate}
            \item Is \verb+git stash clean+ a valid command?
            \item Is \verb+git stash drop+ a valid command?
            \item What flags can be used to show the short version of
                \verb+git status+?
        \end{enumerate}
\end{enumerate}
