\section{About Version Control}
\begin{enumerate}
    \item In Centralized Version Control, there is a single point of
        failure, the server, and if it goes down then nobody can check out
        their code.
    \item In distributed version control, all computers have a full backup
        of the repository, so if something happens to the server,
        information can be copied from a different computer back to the
        server.
\end{enumerate}

\section{A Short History of Git}
\begin{enumerate}
    \item The Linux kernel development community.
    \item 2005
\end{enumerate}

\section{What is Git?}
\begin{enumerate}
    \item Snapshots.
    \item No.
    \item The three states are
        \begin{enumerate}
            \item Modified
            \item Staged
            \item Committed
        \end{enumerate}
\end{enumerate}

\section{The Command Line}
\begin{enumerate}
    \item The command line.
\end{enumerate}

\section{Installing Git}
\begin{enumerate}
    \item This answer will vary, but should take the form x.xx
\end{enumerate}

\section{First-Time Git Setup}
\begin{enumerate}
    \item When using \verb+--global+, you modify your user account only.
        When using \verb+--system+, you modify the entire machine
        configuration.
    \item Your settings can be modified in several different locations.
        As a result, you may have one key with several possible values.
        Checking your configuration settings would clarify what the current
        key value actually is, regardless of which location it comes from.
    \item Set up your git config
        \begin{enumerate}
            \item \verb+git config --global "Your name"+
            \item \verb+git config --global "you@domain.com"+
        \end{enumerate}
    \item \verb+git config user.name+
\end{enumerate}

\section{Getting Help}
\begin{enumerate}
    \item
        \begin{enumerate}
            \item No
            \item Yes
            \item \verb+-s+ and \verb+--short+
        \end{enumerate}
\end{enumerate}
